\MakeUppercase{The Structure of $k$-Planar Graphs}

### 2019-07-11 k-planar.tex
Added a note about David's conjecture

>>>>

\note{PM}{
I'm not sure what the role of $P_1,\ldots,P_{d-1}$ is here.  If the result is true, then for some graph $H$ with $\tw(H)\le f(k,d)$, $G\subseteq H\boxtimes P_1 \boxtimes\dots \boxtimes P_{d-1} \subseteq H\boxtimes P\boxtimes K_{d-1}$  so, $G\subgraph H'\boxtimes P$ where $tw(H')\le f'(k,d):=(f(k,d)+1))(d-1)$ by \cref{MakeWidth1}.  On the other hand, if $G\subgraph H'\boxtimes P$ then $G\subgraph H'\boxtimes P_1\boxtimes\cdots\boxtimes P_{d-1}$ so the two statements are equivalent up to a factor of $d-1$ in $f(k,d)$..
}
